LSOA domestic Electricty and Gas maps

### 2021-09-06 LSOA domestic Elec and Gas.Rmd
added scale free plots & plotted mean kWh change for gas

Solent <- getSolent(LSOAdepelec)
head(Solent)
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y = mean_de_diff_pc, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% change in mean kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs")
```

@@

```{r addFacetsToElecDiff}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff_pc, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change in mean kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

nrow(Solent)
```

@@

nrow(Solent)
```

@@

```{r plotting change in gas usage against dep}
LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
#names(LSOAdepgas)
df <- dplyr::select(LSOAdepgas, LSOA11CD, la_name.x, mean_dg2019, IMDScore, mean_dg2010, IMD_Decile,dg_diff
)

head(df)
df$la_name <- df$la_name.x
Solent <- getSolent(df)
head(Solent)
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/mean_dg2010), 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% change",
       caption = "Mean gas kWh 2010-2019, all Solent LSOas")
```

Try adding facets for each Local Authority and remove the outlier

```{r addFacetsTogasDiff}
# or without colour but using facets for Local Authorities
Solentex <- filter(Solent,100*(dg_diff/mean_dg2010)<50)
ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/mean_dg2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change",
       caption = "Mean gas kWh 2010-2019, all Solent LSOas") +
  facet_wrap(la_name ~ .)

nrow(Solent)
```

@@

```{r Winchester Chnage in LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Winchester")

>>>>

solent_elec <- getSolent(LSOAdepelec)
head(solent_elec)
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y = mean_de_diff_pc, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% change in mean kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs")
```

@@

```{r addFacetsToElecDiff}
# or without colour but using facets for Local Authorities
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff_pc, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change in mean kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

nrow(solent_elec)
```
Plot kWh change as a contrast to % change (which seems constant-ish across IMD)

```{r plotEleckWhchange}
# as a contrast to % change

ggplot(solent_elec, aes(x = mean_de2010, # forces a box plot at each value 
                   y =mean_de_diff,
                   colour = la_name)) +
  geom_point() +
  theme(legend.position="none") +
  geom_smooth() +
  labs(x = "Domestic mean kWh 2010",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs")

# or without colour but using facets for Local Authorities
# first with fixed scales
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

# now with 'free' scales
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ . , scales = "free")

nrow(solent_elec)
```
So there is a slightly downward trend - those in lower deprivation deciles are reducing slightly more.

@@

@@

```{r plotting change in gas usage against dep}
LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
#names(LSOAdepgas)
LSOAdepgas$MSOA_name <- LSOAdepgas$`MSOA Name`
df <- dplyr::select(LSOAdepgas, la_name.x,MSOA_name, LSOA11CD,  IMD_Decile, mean_dg2019, IMDScore, mean_dg2010,mean_dg2019, dg_diff 
)

head(df)
df$la_name <- df$la_name.x
solent_gas <- getSolent(df)
head(solent_gas)
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/mean_dg2010), 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% change",
       caption = "Mean gas kWh 2010-2019, all Solent LSOas")
```

Try adding facets for each Local Authority and remove the outlier where % change > 50

```{r addFacetsTogasDiff}
message("Dropping:")
filter(solent_gas,100*(dg_diff/mean_dg2010)>50)

# or without colour but using facets for Local Authorities
solent_gasex <- filter(solent_gas,100*(dg_diff/mean_dg2010)<50)
ggplot(solent_gasex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/mean_dg2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change",
       caption = "Mean gas kWh 2010-2019, all Solent LSOAs with outlier removed") +
  facet_wrap(la_name ~ .)

nrow(solent_gasex)
```

As for electricity, plot the mean kWh difference. Keep the outlier.

```{r plotGaskWhchange}
# as a contrast to % change

ggplot(solent_gas, aes(x = mean_dg2010, # forces a box plot at each value 
                   y =dg_diff,
                   colour = la_name)) +
  geom_point() +
  theme(legend.position="none") +
  geom_smooth() +
  labs(x = "Domestic mean kWh 2010",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs")

# or without colour but using facets for Local Authorities
# first with fixed scales
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

# now with 'free' scales to see pattern in each LA
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ ., scales = "free")

nrow(solent_gas)
```

@@

```{r Winchester change in LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Winchester")
